\chapter{ANALYSIS}
\label{chap:analysis}
The analysis is optimized to maximize the significance of the final Higgs Boson selected events. 
All events are separated into five categories, three of which are designed to select events associated with the SM Higgs Boson production mechanisms, while the remaining two are tailored to select events associated with neutral MSSM Higgs Boson production mechanisms. 
The separation of the analysis into five separate categories will provide an increased significance in the final result when combined. 
The advantages of the event categorization will be discussed in more detail in Chapter \ref{chap:results}.
Due to the high number of interactions, the first step in the selection of the candidate Higgs boson events is to ensure an efficient trigger path exists to filter signal events from common events, often referred to as minimum bias events.
To protect against additional sources of energy deposits and charged tracks arising from pile-up, a primary vertex with the highest $p_{T}$ sum is selected. 
All charged particles are checked for compatibility with the selected primary vertex.
Once the primary vertex has been selected, high quality muon and tau candidates are selected.
%Once the events have been stored the analysis begins by selecting high quality muon and tau candidates existing in the event.
%Once the muons and taus have been selected a common primary vertex is identified to protect against possible pile-up interference.
The muon, tau objects, and any missing transverse energy are then combined into a composite object that would represent decay products of the originating Higgs Boson.
Finally, additional kinematic variables are used to reject possible backgrounds from $W \rightarrow \mu \nu$, QCD multi-jet, and $Z\rightarrow\mu\mu$ events.

\input{triggerselection}

\input{particleselection}

\input{eventselection}
