\section{Background Estimation}
\label{sec:backgroundestimation}
\newcommand{\bgextrap}{N_{signal}^{MC}/N_{control}^{MC}}
In estimating the backgrounds present in the final event selection two factors are considered separately, the normalization and the shape.
Treating these issues separately allows the backgrounds to be estimated in a data-driven way more so than if the two were taken at the same time.

Where the statistics allow, the background normalization is taken by extrapolating the number of events in the control region to the number of events in the signal region.
This is done by comparing the event yield between the control and signal regions in simulation.
The correction factor is then applied to the control region as measured in the data to produce the estimated background mass distribution.
This technique can fail in the case where either the control and/or signal region do not have a sufficient number of events, in this case the normalization used is taken from the measured luminosity and the cross section for the process as measured by the CMS Collaboration.
Additionally, no control region is available for the $Z \rightarrow \tau\tau$ or the di-boson backgrounds, as such the normalization is taken from the measured luminosity and measured cross sections.

The shape for a given background is taken from the shape of the mass distribution in the control regions as defined in Section \ref{sec:backgrounds}.
A summary of the source for the background shapes can be found in Table \ref{tab:backgroundshapes}, where $\circ$ signifies that the standard analysis cut from Section \ref{chap:analysis} is used, and a $-$ signifies that the cut is not used. 
In Table \ref{tab:backgroundshapes}, it should be noted that $M_{T}$ is only used in the SM search categories, while $\pzetadiff$ is only used in the MSSM search categories.
The normalization techniques used are summarized in Table \ref{tab:backgroundnormalizations}, where CMS $\sigma$ signifies that CMS measured cross section is used, and $\bgextrap$ signifies that the normalization is extrapolated from the control region.

\begin{sidewaystable}[!ht]
\begin{center}
\caption{BACKGROUND CONTROL REGION DEFINITIONS}
\label{tab:backgroundshapes}
\begin{small}
\begin{tabular}{lcccccc}
\toprule
Cut & Analysis & $Z \rightarrow ll$ & $Z \rightarrow \mu\mu$ (Jet)& $W \rightarrow l\nu$ & $t\overline{t}$ & QCD\\
\midrule 
%                                    Standard  Z->ll         Z->llJet      W                        ttbar     QCD
Kinematic/Acceptance Cuts         & $\circ$  & $\circ$  & $\circ$ & $\circ$                & $\circ$ & $\circ$              \\
Relative Lepton Isolation         & $< 10\%$ & $< 5\%$  & $< 5\%$ & $\circ$                & $\circ$ & $10..30\%$           \\
Tau ID                            & Loose    & $\circ$  & $\circ$ & Very-Loose \& !Medium   & $\circ$ & Very-Loose \& !Medium \\
Tau Muon Veto	                  & $\circ$  & inverted & $\circ$ & $\circ$                & $\circ$ & $\circ$              \\
$\Delta R$                        & $\circ$  & $\circ$  & $> 1.0$ & $\circ$                & $\circ$ & $\circ$              \\
$M_{T}$                           & $\circ$  & $\circ$  & $\circ$ & $> 50 GeV$             & $\circ$ & $\circ$              \\
$\pzetadiff$                      & $\circ$  & -        & $\circ$ & $< -30 GeV$            & $\circ$ & -                  \\
$\mu\mu$ Veto                     & $\circ$  & $\circ$  & $\circ$ & $\circ$                & $\circ$ & $\circ$              \\
Zero Charge                       & $\circ$  & $\circ$  & -       & -                      & $\circ$ & -                    \\
$N_{jets}$ w/ $E_{T}>40$ GeV $>2$ & -        & -        & -       & -                      & $\circ$ & -                    \\
B-tagged jet w/ $E_{T}>60$ GeV    & -        & -        & -       & -                      & $\circ$ & -                    \\
$N_{jets}$ w/ $E_{T}>60$ GeV $>1$ & -        & -        & -       & -                      & $\circ$ & -                    \\
\bottomrule
\end{tabular}
\end{small}
\end{center}
\end{sidewaystable}

\begin{table}[!ht]
\begin{center}
\caption{BACKGROUND NORMALIZATION TECHNIQUES}
\label{tab:backgroundnormalizations}
\begin{tabular}{lccccc}
\toprule
\multicolumn{1}{c}{ } &  \multicolumn{3}{c}{Standard Model}  & \multicolumn{2}{c}{MSSM} \\
\midrule
Process                       & {\zeroJets}  &  {\boosted}  &  {\vbf}      &  {\woBtag}   &  {\wBtag} \\
\midrule
$Z \rightarrow \tau\tau$     & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ \\
QCD                           & OS/SS        & OS/SS        & OS/SS        & OS/SS        & OS/SS        \\
$W$+jets 	              & $\bgextrap$  & CMS $\sigma$ & CMS $\sigma$ & $\bgextrap$  & CMS $\sigma$  \\
$Z \rightarrow \mu\tau_{\mu}$ & $\bgextrap$  & CMS $\sigma$ & CMS $\sigma$ & $\bgextrap$  & CMS $\sigma$ \\
$Z \rightarrow \mu\tau_{jet}$ & $\bgextrap$  & CMS $\sigma$ & CMS $\sigma$ & $\bgextrap$  & CMS $\sigma$ \\
$t\bar{t}$                    & $\bgextrap$  & CMS $\sigma$ & CMS $\sigma$ & $\bgextrap$  & CMS $\sigma$ \\
Di-Boson                      & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ & CMS $\sigma$ \\
\bottomrule
\end{tabular}
\end{center}
\end{table}


