\section{Selected Events}
\label{sec:selectedevents}
In the $4.7fb^{-1}$ of $7$ TeV data collected by CMS in 2011 the event yields for the SM categories \emph{Zero/One Jets}, \emph{Boost}, and \emph{VBF} categories were $45714$, $446$, and $130$, respectively. 
The expected background yields provide a total of $45381$, $449$, and $168$, a summarization is given in Table \ref{tab:eventyields}.
Finally the expected signal yields for a SM Higgs boson with a mass of $125$ GeV are $87$, $7$, and $4$, these and other mass points can be seen in Table \ref{tab:smsignalyields}.

\begin{table}[htpb]
  \begin{center}
    \caption{EVENT YIELDS}
    \label{tab:eventyields}
    \begin{tabular}{lccccc}
      \toprule
      process                    	&	Zero/One Jet    	&	Boost        	&	VBF         	&	Non B-Tag        	&	B-Tag          	\\	
      \midrule
      di-boson                    	&	$179 \pm 30$    	&	$4 \pm 0.36$    	&	$0 \pm 0.09$   	&	$136 \pm 23$     	&	$2 \pm 0.2$      	\\	
      $t\overline{t}$               	&	$128 \pm 5$     	&	$108 \pm 24$ 	&	$27 \pm 8$  	&	$49 \pm 0.67$       	&	$91 \pm 2$     	\\	
      $Z\rightarrow\mu\mu$           	&	$410 \pm 0.12$     	&	$1 \pm 0.001$    	&	$0 \pm 0.001$   	&	$389 \pm 0.1$      	&	$4 \pm 1$      	\\	
      $Z\rightarrow\mu jet$         	&	$615 \pm 135$   	&	$2 \pm 0.16$    	&	$4 \pm 0.8$   	&	$572 \pm 119$    	&	$1 \pm 0.59$      	\\	
      QCD Multi-jet                 	&	$6369 \pm 2083$ 	&	$36 \pm 27$  	&	$25 \pm 4$  	&	$5026 \pm 1399$  	&	$161 \pm 13$   	\\	
      $W\rightarrow l\nu$           	&	$8892 \pm 900$  	&	$71 \pm 99$  	&	$43 \pm 26$ 	&	$8507 \pm 930$   	&	$97 \pm 139$   	\\	
      $Z\rightarrow\tau\tau$        	&	$28786 \pm 2427$	&	$223 \pm 96$ 	&	$66 \pm 9$  	&	$30763 \pm 2888$ 	&	$299 \pm 129$  	\\	
      \midrule
      Total Background              	&	$45381 \pm 3326$	&	$448 \pm 143$	&	$167 \pm 29$	&	$45446 \pm 3343$ 	&	$658 \pm 191$  	\\	
%      $H/\phi\rightarrow\tau\tau$	&	$87 \pm 15$      	&	$7 \pm 2$ 	&	$4 \pm 0.76$	&	$4691 \pm 412$  	&	$510 \pm 47$	\\	
      Observed                   	&	$45714$         	&	$446$        	&	$130$       	&	$43007$          	&	$630$          	\\	
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table}[htpb]
  \begin{center}
    \caption{EXPECTED SM SIGNAL YIELDS}
    \label{tab:smsignalyields}
    \begin{tabular}{lccc}
    \toprule
    Mass [GeV]	&	\emph{Zero/One Jet}	&	\emph{Boost}	&	\emph{VBF}  	\\	
    \midrule
    $100$     	&	$266 \pm 68$       	&	$21 \pm 8$  	&	$10 \pm 2$  	\\	
    $105$     	&	$253 \pm 64$       	&	$19 \pm 7$  	&	$10 \pm 2$  	\\	
    $110$     	&	$121 \pm 22$       	&	$8 \pm 2$   	&	$5 \pm 1$   	\\	
    $115$     	&	$119 \pm 21$       	&	$8 \pm 2$   	&	$5 \pm 0.97$	\\	
    $120$     	&	$101 \pm 18$       	&	$7 \pm 2$   	&	$4 \pm 0.85$	\\	
    $125$     	&	$87 \pm 15$        	&	$7 \pm 2$   	&	$4 \pm 0.76$	\\	
    $130$     	&	$75 \pm 13$        	&	$5 \pm 1$   	&	$3 \pm 0.62$	\\	
    $135$     	&	$61 \pm 11$        	&	$4 \pm 1$   	&	$2 \pm 0.49$	\\	
    $140$     	&	$45 \pm 8$         	&	$3 \pm 0.90$	&	$2 \pm 0.43$	\\	
    $145$     	&	$32 \pm 5$         	&	$2 \pm 0.69$	&	$1 \pm 0.31$	\\	
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

In the MSSM search categories \emph{Non B-Tagged} and \emph{B-Tagged}, the event yields in the data were $43007$ and $630$ respectively.
The expected background yields are estimated to be $45446$ and $658$, while the expected signal yields for a neutral Higgs Boson (A) with mass $120$ GeV and $\tan\beta = 30$ are $4691$, and $510$.
Expected signal yields for other mass points in the MSSM search can be seen in Table \ref{tab:mssmsignalyields}. 
The table lists yields where $tan\beta = 30$.
The expected signal yields are normalized to the predicted cross sections for the three neutral Higgs bosons.
For masses less than $130$ GeV the yield is normalized to the combined predicted cross sections for the light CP-even Higgs boson and the CP-odd Higgs boson.
For masses greater than $130$ GeV the yield is normalized to the combined predicted cross sections for the heavy CP-even Higgs boson and the CP-odd Higgs boson.
At the mass point of $130$ GeV all predicted cross sections are taken into account for the normalization.
The combination of predicted cross sections in calculating the normalization of the expected signal yield corresponds to the CP-odd Higgs boson being degenerate in mass with either the light or heavy CP-even Higgs boson.

\begin{table}[htpb]
  \begin{center}
    \caption{EXPECTED MSSM SIGNAL YIELDS}
    \label{tab:mssmsignalyields}
    \begin{tabular}{lcc}
    \toprule
    Mass [GeV]	&	\emph{Non B-Tag}	&	\emph{B-Tag}	\\	
    \midrule
    $100$     	&	$6944 \pm 610$  	&	$583 \pm 54$	\\	
    $120$     	&	$4691 \pm 412$  	&	$510 \pm 47$	\\	
    $130$     	&	$4132 \pm 363$  	&	$449 \pm 41$	\\	
    $140$     	&	$3069 \pm 269$  	&	$372 \pm 34$	\\	
    $160$     	&	$2157 \pm 189$  	&	$296 \pm 27$	\\	
    $180$     	&	$1439 \pm 126$  	&	$217 \pm 20$	\\	
    $200$     	&	$929 \pm 81$    	&	$155 \pm 14$	\\	
    $250$     	&	$303 \pm 26$    	&	$49 \pm 4$  	\\	
    $300$     	&	$84 \pm 7$      	&	$14 \pm 1$  	\\	
    $350$     	&	$22 \pm 2$      	&	$3 \pm 0.36$	\\	
    $400$     	&	$8 \pm 0.71$    	&	$1 \pm 0.11$	\\	
    $450$     	&	$3 \pm 0.28$    	&	$0 \pm 0.05$	\\	
    $500$     	&	$1 \pm 0.12$    	&	$0 \pm 0.02$	\\	
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

The data is compatible with the background only hypothesis in all categories when taking into account statistical and systematic uncertainties.
The final selected muon and tau $p_{T}$ and $\eta$ distributions for each category can be found in Figures \ref{fig:finalleptonzerojets}, \ref{fig:finalleptonboosted}, \ref{fig:finalleptonvbf}, \ref{fig:finalleptonwobtag}, and \ref{fig:finalleptonwbtag}. 
The final selected mass distributions can be found in Figures \ref{fig:smmasszerojets}, \ref{fig:smmassboosted}, \ref{fig:smmassvbf}, \ref{fig:mssmmasswobtag}, and \ref{fig:mssmmasswbtag}.
In each of the plots, the expected mass distribution for the Higgs boson has been overlaid atop the distribution to demonstrate the magnitude a signal would have were it found.
The mass of the Higgs boson shown has a mass of $125$ GeV for the SM categories and $120$ GeV for the MSSM categories.
In the case of the SM categories the signal distribution is multiplied by a factor of five to increase readability.


