\section{The Standard Model}
\label{sec:standardmodel}
The standard model (SM) is a quantum field theory that exists as the synthesis of three gauge symmetries representing the electromagnetic, weak, and strong nuclear interactions.
The electromagnetic interaction is described by quantum electrodynamics (QED) and accurately describes the interactions of light and matter. % FIXME REF
The weak interaction was developed to explain the process of nuclear decay.
The strong interaction has been very successful in describing the dynamics that bind the nuclei of atoms via quantum chromodynamics.
Although developed separately, these three theories combine to make very accurate predictions of the physical phenomena found in elementary particle physics. 
Together they are the established theory of elementary particle physics.

Beyond treating the three previously mentioned theories together, a concerted effort has been put forth to unify the three theories into a combined ``Theory of Everything'' or grand unified theory (GUT).
The first step taken in producing a GUT was taken by finding a means of combining the electromagnetic and weak interactions into the combined electroweak theory. %~\cite{GLASHOW} ~\cite{WEINBERG} ~\cite{SALEM}(FIXME REF).
The combined electroweak theory is a gauge theory with massless gauge bosons and a combined symmetry that is broken via the Higgs mechanism resulting in the separate electromagnetic and weak theories.
The Higgs mechanism carries with it the result that an additional massive boson is produced, and it is the search for this boson which will be the topic of interest in the following analysis.

%\input{sm}
%\input{electroweak}
\input{qed}

\input{weak}

\input{qcd}

\input{spontaneous}
